taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-02-28 paper/manuscript.Rmd
WIP
support for synonyms

```{r message=FALSE}
bbs <- read_tsv(system.file("extdata/bbs.tsv", package="taxadb"))
```

```{r}
dim(bbs)

```{r}
bbs_ids <- 
bbs %>% 
  select(species) %>%
  mutate(
         gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd", "prefix"),
         iucn = get_ids(species, "iucn", "prefix"),
          ott = get_ids(species, "ott","prefix") 
  )

@@

```{r}
unmatched$input %>% ids("iucn") %>% 
  select(scientificName, taxonomicStatus, input, taxonID, acceptedNameUsageID)

syn <- taxa_tbl("iucn") %>% 
  right_join(
    unmatched$input %>% 
    ids("iucn") %>% 
    select(acceptedNameUsageID),
    copy = TRUE) %>%
  select(scientificName, acceptedNameUsageID, taxonomicStatus) %>%
  collect()

## Some names have multiple synonyms, do not do this as a spread...    
syn %>% mutate(n = 1:length(scientificName)) %>% spread(taxonomicStatus, scientificName)
```

>>>>

```{r message=FALSE}
bbs <- read_tsv(system.file("extdata/bbs.tsv", package="taxadb"))
dim(bbs)
```

```{r}
bbs_ids <- 
bbs %>% 
  select(species) %>%
  mutate(
         gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col",  "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd",   "prefix"),
         iucn = get_ids(species, "iucn", "prefix"),
          ott = get_ids(species, "ott",  "prefix") 
  )

@@

```{r}
syn <- unmatched$input %>% synonyms("iucn")
syn
```

Three of these synonyms are considered accepted names in OTT:

```{r}
syn$synonym %>% na.omit() %>% ids("ott")
```

```{r}
syn$synonym %>% na.omit() %>% get_ids("ott")
syn %>% na.omit() %>% mutate(
  #ott = get_ids(synonym, "ott"),
                             col = get_ids(synonym, "col"),
                             itis = get_ids(synonym, "itis"),
                             gbif = get_ids(synonym, "gbif"))
```

syns <- unmatched$input %>% ids("iucn") %>%
        dplyr::filter(taxonomicStatus != "accepted") %>%
        dplyr::select(synonym = scientificName,
                      synonym_id = taxonID,
                      taxonomicStatus,
                      acceptedNameUsageID)
accepted

syn <- unmatched$input %>% synonyms("iucn")
syn
```
